---
output:
  md_document:
    variant: markdown_github
---
```{r global_options, echo=FALSE}
knitr::opts_chunk$set(fig.path='figure/', warning=FALSE, message=FALSE, error=FALSE)
```
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)

```

# HistDAWass 1.0.7 What’s new

Minor bug fixes fo compatibility isseues with ggridges.

# HistDAWass 1.0.6 What's new

Added the WH_WASS_MAT_DIST for computing a distance matrix

# HistDAWass 1.0.5 What's new

Fixed some minor bugs. Added the names of columns and the rows in weights matrices of adaptive distances based methods. 


# HistDAWass 1.0.4 What's new

Fixed some minor bugs.


# HistDAWass 1.0.3 What's new

## Histogram-valued Data analysis using Wasserstein metric

Fixed some visualizations accordingly to the new ggplot2 release.


#HistDAWass 1.0.2 What's new
##(Histogram-valued Data analysis using Wasserstein metric)

Soelf Organizing maps have been improved for speed and aptions.

#HistDAWass 1.0.1 What's new
##(Histogram-valued Data analysis using Wasserstein metric)

Some bugs have been resolved when processing data with a single variable.

#HistDAWass 1.0.0 What's new
##(Histogram-valued Data analysis using Wasserstein metric)

Now, a set of methods for MatH (WH.SSQ, WH.vec.mean, and all the methods using them) are much faster due to RCPP implementation.

#HistDAWass 0.1.7 What's new
##(Histogram-valued Data analysis using Wasserstein metric)

Some general improvements have been added for reducing elaboration times.
 
> unsupervised learning

WH_kmeans now returns more informative outputs

> principal components analysis

Multiple factor analysis has new functions for plotting results

#HistDAWass 0.1.6 What's new
##(Histogram-valued Data analysis using Wasserstein metric)

> unsupervised learning

fuzzy c-means and kohonen maps are 10 times faster

#HistDAWass 0.1.5 What's new
##(Histogram-valued Data analysis using Wasserstein metric)

> some minor bug fixed


#HistDAWass 0.1.4 What's new
##(Histogram-valued Data analysis using Wasserstein metric)

> some minor bug fixed

#HistDAWass 0.1.3 What's new
Some fixes to the worksapce

#HistDAWass 0.1.2 What's new
##(Histogram-valued Data analysis using Wasserstein metric)
> From raw data to histograms    

A new function was added for generating a histogram from a set of raw data

> Visualization    

Now for plotting, `ggplot2` package is used generally.

A new plot for visualizing Histogram Time Series was added.

A new plot for comparing obversed vs predicted histogram was added.

A new plot for showing the differences between an observed and a predicted histogram was added.

> Regression and predictive techniques

A new function for computing Goodness of Fit of a model was added 

